---
title: "USM Office of Marketing and Brand Management"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"

output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(blastula)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)


# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)
```


# **FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns**

# Description

`r newthought('The purpose of this report')` is identify how the weekly Admission's Reports generated by John Tabor can inform Marketing's digital advertising efforts.

There are between 10 and 14 reports furnished to us weekly and I endeavor to point to the most useful reports that would assist in optimizing our various campaigns. 

# Findings

**Agency Campaigns**

1.  Undergraduate Programs for In-State High School Students
2.  Undergraduate Out-of-State High School Students
3.  Transfer Program for Current Undergraduates
4.  Degree Completion for Working Adults
5.  Graduate Programs for Current Undergraduates
6.  Graduate Programs for Working Adults
7.  Online Programs
8.  Special Programs

`r newthought('The table below')` identifies where the information can be found in the weekly reports.

```{r}
Table <-  read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Segments.csv", header = T, stringsAsFactors = F)
```

```{r}
kable(Table)
```
install.packages("magick")
install.packages("webshot")

# Conclusions

- I propose sharing a simple table on a weekly basis. 


```{r}
library(gridExtra)
library(kableExtra)
library(magick)
library(webshot)
#webshot::install_phantomjs()
```

library(gridExtra)

df = data.frame("variables" = c("d_agr","d_def","d_frig","d_hidro","d_roads","d_silos"),
"coeficient" = c(0.18,0.19,-0.01,-0.25,-0.17,0.09))

png("output.png", width=480,height=480,bg = "white")
grid.table(df)
dev.off()

```{r}
Sample <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Sample.csv", header = T, stringsAsFactors = F)
png("output.png", width=480,height=480,bg = "white")
grid.table(Sample)
dev.off()
kable(Sample)
```

- It will take about one hour weekly to summarize the findings in the multiple admissions' reports.

- Notes after rough draft discussion
  - Clarify classification of stealth apps
  - Clarification of other elements detailed in email to John Tabor. 
  - Final report should have weekly ups and downs by numbers and percentages. 
  - Add form completions for direct conversions. 


\href{https://www.wrike.com/open.htm?id=569449783}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/FY21-Weekly-Admissions-Reports-Summary}{{\color{blue}{\underline{Github Repository}}}}



```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
