---
title: "FY21 Q1 Admissions Funnel Summary for Advertising"
author: "Office of Marketing and Brand Management"
date: "10/13/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r}
library(tidyr)
library(dplyr)
library(kableExtra)
```

# Brief Description:

The following report provides 2 summaries. First, I show a succinct version of the Weekly Admission's Reports put together by John Tabor, Associate Director of Communications & Analytics at the University of Southern Maine. This report is condensed to include only the number of inquiries and applications Admissions has seen to date for the FA21 and FA20 cycles. The second table is a summary of the number of completed inquiry forms as an initial referral source. Forms are completed by digital ad viewers who have navigated to __request more information__.

# Findings

## Admissions Funnel Summary through September 21, 2020 (most current)

```{r eval=FALSE, include=FALSE}
`PH_20-19-18` <-  c(740L, 1376L, 3628L)
`JR_20-19-18` <- c(3890L, 8944L, 11736L)
`SR_20-19-18` <- c(13670L, 15656L, 13311L)


`OOS_PH_20` <- c(552L, 1072L, 3127L)
`OOS_JR_20` <- c(3049L, 6171L, 8064L)
`OOS_SR_20` <- c(9191L, 10875L, 9231L)


`TR_R_20-19-18` <- c(2183L, 2112L, 2246L)
`TR_S-20-19-18` <- c(15853L, 17768L, 15557L)


`GR_20-19-18` <- c(1641L, 1217L, 1157L)
`OOS_GR_20` <- c(534L, 320L, 291L)


`FY_Over25_20` <- c(1000L, 1048L, 1162L)


newBeforeSept_1 <- rbind.data.frame(`PH_20-19-18`, 
                                    `OOS_PH_20`,
                                    `JR_20-19-18`, 
                                    `OOS_JR_20`, 
                                    `SR_20-19-18`,
                                    `OOS_SR_20` ,
                                    `TR_R_20-19-18`,
                                    `TR_S-20-19-18`,
                                    `GR_20-19-18`,
                                    `OOS_GR_20`,
                                    `FY_Over25_20` 
)

newBeforeSept_1 <- newBeforeSept_1 %>% mutate(RecruitingPeriod = "Fall_2020")
newBeforeSept_1




IS_HS_UG_20 <- 50L+ 218L + 916
IS_HS_UG_19 <- 82L+373L+2965L

IS_HS_UG_20
IS_HS_UG_19

IS_HS_All <- cbind.data.frame(IS_HS_UG_19, IS_HS_UG_20)
IS_HS_All <- IS_HS_All %>% mutate(chg_19_20 = round((IS_HS_UG_20 - IS_HS_UG_19)/IS_HS_UG_19,2)*100, 
                            IS_HS_UG_19 = prettyNum(IS_HS_UG_19,big.mark = ","), 
                            IS_HS_UG_20 = prettyNum(IS_HS_UG_20, big.mark = ","),
                            chg_19_20 = paste0(chg_19_20, "%"))
IS_HS_All

OOS_HS_UG_20 <- 122L+ 681L+ 3321L
OOS_HS_UG_19 <- 139L+1147L+6431L

OOS_HS_UG_20
OOS_HS_UG_19

OOS_HS_All <- cbind.data.frame(OOS_HS_UG_19, OOS_HS_UG_20)
OOS_HS_All <- OOS_HS_All %>% mutate(chg_19_20 = round((OOS_HS_UG_20 - OOS_HS_UG_19)/OOS_HS_UG_19,2)*100, 
                           OOS_HS_UG_19 = prettyNum(OOS_HS_UG_19,big.mark = ","), 
                           OOS_HS_UG_20 = prettyNum(OOS_HS_UG_20, big.mark = ","),
                           chg_19_20 = paste0(chg_19_20, "%"))
OOS_HS_All
```


```{r }
negs <- c("-65%", "45%", "-57%", "-45%", "-72%", "-57%", "-18%", "-14%")

numbers <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Reports/Number_9-21.csv", header = T, stringsAsFactors = F)


kable(numbers)%>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Inquiries" = 2, "Applicants" = 2, "YoY Change" = 2))
```

## Marketing Forms as an Initial Inquiry Source  (July 1 - September 30)

```{r}

inqs2 <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Reports/TY1Better.csv", header = T, stringsAsFactors = F)

inqs2 <- inqs2 %>% mutate(Initial.Source.Date = as.Date(Initial.Source.Date, format = "%m/%d/%Y"))

inqs2$Audience <- factor(inqs2$Audience, levels = c("HS-IS", "HS-OOS", "HS-UNKN", "TR", "WA", "GR", "OL"))
kable(inqs2 %>% 
        mutate(FY = ifelse(Initial.Source.Date < "2020-06-30", "FY20", "FY21")) %>% 
        group_by(Audience, FY) %>% summarise(Inqs = n()) %>% 
        spread(FY, Inqs) %>% select(Audience, FY21, FY20) %>% mutate(Change = paste0(round((FY21-FY20)/FY20*100,2), "%")) %>% 
        na.omit())%>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Inquiries" = 2, " " = 1))
```
\newpage

# Conclusions

* Overall inquiries for Fall 2021 start. 

* Marketing inquiries are also down as a whole, however they are up for both in-state HS students seeking an Undergraduate degree and students interested in an Online program. There is currently no way to count Online degree inquiries, but we see applications are up a lot. 

* Applications are slightly up for most audiences. 

#

\href{https://www.wrike.com/open.htm?id=569449783}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/FY21-Weekly-Admissions-Reports-Summary}{{\color{blue}{\underline{Github Repository}}}}


