---
title: "Inquiries_by_Week"
author: "Office of Marketing and Brand Management"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```



### Description

On 10/29/20 USM Marketing met with Rinck Advertising's Media Team to discuss the Admission's data they would like to incorporate into the Advertising Dashboards.

Today we realized that the Inquiry Summary distributed by Admissions does not exactly capture the information they are looking for. They would like to have a weekly report that they can overlay the ad vendor performance reports, i.e., a week to week record of the inquiries as they come in for each audience and product.

Audience and Product have been previously defined by Tracy St. Pierre, as follows:

HS students > UG degree
Transfers > UG degree
Online students > UG Degree (typically transfers or Working Adults)
Degree Completers > UG degree
Current UG > Graduate degree
Working adults > Graduate degree
Online students > Graduate degree (typically working adults)

```{r}
library(tidyverse)
library(knitr)
```

```{r}
DAA <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Reports/DAA_10-28-2020.csv", header = T, stringsAsFactors = F)
names(DAA)
```
## Factor Values

### Student Type


```{r}
unique(DAA$Student.Type)
```

### Student Stage


```{r}
unique(DAA$Student.Stage)
DAA <- DAA %>% mutate(Student.Stage = ifelse(grepl("Applic", Student.Stage), "Applicant", Student.Stage))
```

### Anticipated Start


```{r}
unique(DAA$Anticipated.Start.Term.Year)

DAA <- DAA %>% 
  mutate(Anticipated.Start.Term.Year= 
                        ifelse(Anticipated.Start.Term.Year == "Sep-18", "Fall 2018",
                               ifelse(Anticipated.Start.Term.Year == "Sep-19", "Fall 2019", 
                                      ifelse(Anticipated.Start.Term.Year == "Jan-19", "Spring 2019", 
                                             ifelse(Anticipated.Start.Term.Year == "Summer 2021 2021", "Fall 2021", 
                                                    ifelse(Anticipated.Start.Term.Year == "Jan-18", "Spring 2018", 
                                                           ifelse(Anticipated.Start.Term.Year == "2018", "Fall 2018", 
                                                                  ifelse(Anticipated.Start.Term.Year == "2020", "Fall 2020", 
                                                                         ifelse(Anticipated.Start.Term.Year == "Spring 2021 2021", "Spring 2021", 
                                                                                ifelse(Anticipated.Start.Term.Year == "Spring 2019 2019", "Spring 2019", 
                                                                                       ifelse(Anticipated.Start.Term.Year == "Summer 2022 2022", "Fall 2022", 
                                                                                              ifelse(Anticipated.Start.Term.Year == "Spring 2022 2022", "Spring 2022", 
                                                                                                     ifelse(Anticipated.Start.Term.Year == "Summer 2023", "Fall 2023", ifelse(Anticipated.Start.Term.Year == "Summer 2019 2019", "Fall 2019", 
                                                                                                                                                                              ifelse(Anticipated.Start.Term.Year == "Fall 2020 2020", "Fall 2020", 
                                                                                                                                                                                     ifelse(Anticipated.Start.Term.Year == "Fall 2021 2021", "Fall 2021",
                                                                                                                                                                                            ifelse(Anticipated.Start.Term.Year == "Summer 2020", "Fall 2020", 
                                                                                                                                                                                                   ifelse(Anticipated.Start.Term.Year == "Summer 2019", "Fall 2019", 
                                                                                                                                                                                                          ifelse(Anticipated.Start.Term.Year == "Summer 2021", "Fall 2021", 
                                                                                                                                                                                                                 ifelse(Anticipated.Start.Term.Year == "Summer 2018", "Fall 2018", 
                                                                                                                                                                                                                        ifelse(Anticipated.Start.Term.Year == "Summer 2022", "Fall 2022", 
                                                                                                                                                                                                                               ifelse(Anticipated.Start.Term.Year == "Fall 2022 2022", "Fall 2022", Anticipated.Start.Term.Year))))))))))))))))))))) )
#unique(DAA$Anticipated.Start.Term.Year)
```

### Application Status


```{r}

AppliedCats <- c("Withdrawn (Before Decision)", "Incomplete", "Hold (More Information Needed)", "Denied", "Complete (No Decision)", "Complete (Waitlisted)") 


DAA <- DAA %>% 
  mutate(App.Application.Status = 
           ifelse(App.Application.Status %in% AppliedCats, "Applied",
                  ifelse(grepl("Confirm", App.Application.Status), "Confirmed",
                          ifelse(grepl("Enrolled", App.Application.Status), "Enrolled", 
                                 ifelse(grepl("Admit", App.Application.Status), "Admitted", App.Application.Status)))))

unique(DAA$App.Application.Status)
```

### Student Age Group at Time of Inq/App


```{r}
#unique(DAA$Age)
```

### Stealth Apps


```{r}

DAA <- DAA %>% 
  mutate(Stealth = ifelse(Initial.Referral.Source == "APPL", "Stealth", "Not Stealth"))
#unique(DAA$Stealth)
#DAA %>% group_by(Career, Student.Type) %>% summarise(n = n())


```

```{r}
kable(DAA %>% 
        filter(Student.Type == " ") %>% 
        select(Student.Type, Career, Student.Stage))
```

[Wrike Notes](https://www.wrike.com/open.htm?id=586459551)

[Wrike Project for Chris](https://www.wrike.com/open.htm?id=586545629)

[Github Project for Chris](https://github.com/edithbird/FY21-Weekly-Admissions-Reports-Summary)
