---
title: "Inquiries_by_Week"
author: "Office of Marketing and Brand Management"
date: "10/29/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```



### Description

On 10/29/20 USM Marketing met with Rinck Advertising's Media Team to discuss the Admission's data they would like to incorporate into the Advertising Dashboards.

Today we realized that the Inquiry Summary distributed by Admissions does not exactly capture the information they are looking for. They would like to have a weekly report that they can overlay the ad vendor performance reports, i.e., a week to week record of the inquiries as they come in for each audience and product.

Audience and Product have been previously defined by Tracy St. Pierre, as follows:

- <input type="checkbox" unchecked> Venus</input>
- <input type="checkbox" checked> Mars</input>

HS students In-State
HS students OOS

Transfers > UG degree (19-23 and Unknown) Tell Tracy that this drastically changes the numbers we saw last time.In-State

Transfers > UG degree (19-23 and Unknown) Tell Tracy that this drastically changes the numbers we saw last time. OOS 



Degree Completers > UG degree

Online students > UG Degree (typically transfers or Working Adults)

Current UG > Graduate degree

Working adults > Graduate degree

Online students > Graduate degree (typically working adults)

```{r}
library(tidyverse)
library(knitr)

```

```{r}
# Read data
#MacOnly 

DAA <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Reports/DAA_12-01-2020.csv", header = T, stringsAsFactors = F)
Date <- Sys.Date()
#WINDOWS

#DAA <- read.csv("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/Reports/DAA_11-13-2020.csv", header = T, stringsAsFactors = F)
```

```{r}
# Convert dates
DAA1 <- DAA %>% 
  mutate_at(
    vars("Birthdate", "App.Application.Date", "Initial.Source.Date", "Created.Date"), 
    as.POSIXct,
    format = "%m/%d/%Y")
```

### Factor Values in Raw Data


### __Fiscal Year Initial Source Date__


```{r}
#create FY variable on initial source date
DAA1 <- DAA1 %>% mutate(
  FiscalYear = ifelse(Initial.Source.Date>="2015-07-01" & Initial.Source.Date <= "2016-06-30", "FY16", 
                      ifelse(Initial.Source.Date>="2016-07-01" & Initial.Source.Date <= "2017-06-30", "FY17",
                             ifelse(Initial.Source.Date>="2017-07-01" & Initial.Source.Date <= "2018-06-30", "FY18",
                                    ifelse(Initial.Source.Date>="2018-07-01" & Initial.Source.Date <= "2019-06-30", "FY19",
                                           ifelse(Initial.Source.Date>="2019-07-01" & Initial.Source.Date <= "2020-06-30", "FY20",
                                                  ifelse(Initial.Source.Date>="2020-07-01" & Initial.Source.Date <= "2021-06-30", "FY21","FY15 or earlier")))))))

```



### __Student Type__


```{r}
#if student type is and the student is a lead, we can assume this a a first-year student because we only buy leads who are first-year bound. If student type is blank and the career is graduate, the student type will also be graduate.
DAA1 <- DAA1 %>% 
  mutate(Student.Type = ifelse(Student.Stage == "Lead", "First-Year Student",
                               ifelse(Career == "Graduate", "Graduate", Student.Type)))
```

### __Student Stage__


```{r}
#remove leads and classify other student stages
DAA1 <- DAA1 %>% mutate(Student.Stage = ifelse(grepl("Applic", Student.Stage), "Applicant", Student.Stage))
DAA1 <- DAA1 %>% filter(Student.Stage != "Lead")
```

### __Anticipated Start__


```{r}
#tidy up the Start term year choices
DAA1 <- DAA1 %>% 
  mutate(Anticipated.Start.Term.Year= 
                        ifelse(Anticipated.Start.Term.Year == "Sep-18", "Fall 2018",
                               ifelse(Anticipated.Start.Term.Year == "Sep-19", "Fall 2019", 
                                      ifelse(Anticipated.Start.Term.Year == "Jan-19", "Spring 2019", 
                                             ifelse(Anticipated.Start.Term.Year == "Summer 2021 2021", "Fall 2021", 
                                                    ifelse(Anticipated.Start.Term.Year == "Jan-18", "Spring 2018", 
                                                           ifelse(Anticipated.Start.Term.Year == "2018", "Fall 2018", 
                                                                  ifelse(Anticipated.Start.Term.Year == "2020", "Fall 2020", 
                                                                         ifelse(Anticipated.Start.Term.Year == "Spring 2021 2021", "Spring 2021", 
                                                                                ifelse(Anticipated.Start.Term.Year == "Spring 2019 2019", "Spring 2019", 
                                                                                       ifelse(Anticipated.Start.Term.Year == "Summer 2022 2022", "Fall 2022", 
                                                                                              ifelse(Anticipated.Start.Term.Year == "Spring 2022 2022", "Spring 2022", 
                                                                                                     ifelse(Anticipated.Start.Term.Year == "Summer 2023", "Fall 2023", ifelse(Anticipated.Start.Term.Year == "Summer 2019 2019", "Fall 2019", 
ifelse(Anticipated.Start.Term.Year == "Fall 2020 2020", "Fall 2020", 
ifelse(Anticipated.Start.Term.Year == "Fall 2021 2021", "Fall 2021",
    ifelse(Anticipated.Start.Term.Year == "Summer 2020", "Fall 2020", 
           ifelse(Anticipated.Start.Term.Year == "Summer 2019", "Fall 2019", 
                  ifelse(Anticipated.Start.Term.Year == "Summer 2021", "Fall 2021", 
                         ifelse(Anticipated.Start.Term.Year == "Summer 2018", "Fall 2018", 
                                ifelse(Anticipated.Start.Term.Year == "Summer 2022", "Fall 2022", 
                                       ifelse(Anticipated.Start.Term.Year == "Fall 2022 2022", "Fall 2022", Anticipated.Start.Term.Year))))))))))))))))))))))
```

### __Application Status__


```{r}
#group by app status
AppliedCats <- c("Withdrawn (Before Decision)", "Incomplete", "Hold (More Information Needed)", "Denied", "Complete (No Decision)", "Complete (Waitlisted)") 
DAA1 <- DAA1 %>% 
  mutate(App.Application.Status = 
           ifelse(App.Application.Status %in% AppliedCats, "Applied",
                  ifelse(grepl("Confirm", App.Application.Status), "Confirmed",
                          ifelse(grepl("Enrolled", App.Application.Status), "Enrolled", 
                                 ifelse(grepl("Admit", App.Application.Status), "Admitted", App.Application.Status)))))


```

### __Student Age Group at Time of Inq/App__


```{r}
#since we are targeting by age group, we want to see ages at the time of inquiry
DAA2 <- DAA1 %>% mutate(AgeAtInquiry = round(difftime(Initial.Source.Date, Birthdate, units = "weeks"),0), 
                        Age_Y = as.integer(round(AgeAtInquiry/52, 0)), 
                        
                        AgeGroup = 
                          ifelse(Age > 13 & Age_Y <=19, "19 and Under", 
                                 ifelse(Age_Y > 19 & Age_Y < 25, "20-25", 
                                        ifelse(Age_Y >= 25, "26 and Up", "Unknown"))), 
                        AgeGroup = ifelse(is.na(AgeAtInquiry) , "Unknown", AgeGroup), 
                        AgeGroupforTransfers = ifelse(AgeGroup == "Unknown", "Unknown Age",
                                                      ifelse(Age_Y >= 0 & Age_Y < 19, "Too Young", 
                                                        ifelse(Age_Y > 24, "Too Old", 
                                                          ifelse(Age_Y >=19 & Age_Y <= 24, "Transfer Age","Unknown"))))) 
```

### __Region__


```{r}
targetedStates <- c("Massachusetts", "Connecticut", "New Hampshire")
OtherNE <- c("Rhode Island", "Vermont")
DAA2 <- DAA2 %>% mutate(Region = ifelse(Primary.State.Province == "Maine", "Maine", 
                                        ifelse(Primary.State.Province %in% targetedStates, "Targeted OOS", 
                                               ifelse(Primary.State.Province %in% OtherNE, "Other NE", "Remaining USA"))))
```

### __Stealth Apps__



```{r}
suppressPackageStartupMessages(library("dplyr"))
```

```{r}
DAA3 <- DAA2 %>% 
  mutate(Stealth = ifelse(Initial.Referral.Source == "APPL", "Stealth", "Not Stealth"))
#unique(DAA$Stealth)
DAA4 <- DAA3 %>% 
  mutate(Student.Stage = ifelse(Student.Stage == "", "Inquiry", Student.Stage), 
         App.Application.Status = ifelse(App.Application.Status == "" & Student.Stage == "Applicant", "Applied", App.Application.Status ), 
         App.Application.Status = ifelse(App.Application.Status == "" & Student.Stage == "Inquiry", "Inquiry", App.Application.Status)) %>% 
  group_by(Stealth, Career, Student.Type, Anticipated.Start.Term.Year, Student.Stage, App.Application.Status, AgeGroup, Region, FiscalYear, AgeGroupforTransfers) %>% 
  summarise(n = n()) 
```
 
### __Narrow FY__
 
```{r}
SelectFY <- c("Fall 2018", "Fall 2019", "Fall 2020", "Fall 2021")
DAA4 <- DAA4 %>% filter(Anticipated.Start.Term.Year %in% SelectFY)
unique(DAA4$Anticipated.Start.Term.Year)
```

### __Save final tidied data set__

```{r}


DAA4 <- DAA4%>% mutate(DataDate = Date)

#DAA4 <- DAA4%>% mutate(DataDate = Sys.Date())
#Date <- Sys.Date()


#MacOnly

# write.csv(DAA4, paste0("/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/TidiedInqAppReports/InqAndApps_", Date, ".csv", row.names(F)))


# Windows
write.csv(DAA4, paste0("C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/TidiedInqAppReports/InqAndApps_", Date, ".csv", row.names(F)))
```


## Inquiries


### 1 Undergraduate Degree for In-State High School Students Inquiries



```{r}

One <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Maine" & 
           #Student.Stage == "Inquiry" & 
           Career == "Undergraduate" & 
           Student.Type == "First-Year Student" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup == "19 and Under")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "HSUGIS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)

```

### 2 Undergraduate Degree for Out-of-State High School Students Inquiries



```{r}
Two <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Targeted OOS" & 
           #Student.Stage == "Inquiry" & 
           Career == "Undergraduate" & 
           Student.Type == "First-Year Student" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup == "19 and Under")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "HSUGOS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

### 3 Transfer In-State Inquiries

```{r}
#AgeGroupforTransfers


AgeTransfers <- c("Unknown Age", "Transfer Age")
Three <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
         Region == "Maine" & 
         Career == "Undergraduate" & 
         Student.Type == "Transfer" & grepl("^Fall", Anticipated.Start.Term.Year),
         AgeGroupforTransfers %in% AgeTransfers)  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "CUTRIS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

### 4 Transfer Out-of-State Inquiries
 
```{r}
Four <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Targeted OOS" & 
           Career == "Undergraduate" & 
           Student.Type == "Transfer" & 
           grepl("^Fall", Anticipated.Start.Term.Year)&
           AgeGroupforTransfers %in% AgeTransfers)  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant) + sum(Inquiry), Aud_P = "CUTROS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

### 5 Working Adults Inquiries


```{r}
filterForWA <- c("26 and Up", "Unknown")
Five <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           #Region == "Maine" & 
           #Student.Stage == "Inquiry" & 
           Career == "Undergraduate" & 
           #Student.Type == "First-Year Student" & 
           grepl("^Fall", Anticipated.Start.Term.Year) &
           AgeGroup %in% filterForWA)  %>% 
  group_by( Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "WADC") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

### 6 Inquiries Graduate In-State Current Undergrads

```{r}
Six <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Maine" & 
           #Student.Stage == "Inquiry" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup == "20-25")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "CUGRIS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

### 7 Inquiries Graduate In-State Working Adults

```{r}
Seven <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Maine" & 
           #Student.Stage == "Inquiry" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year)&
           AgeGroup == "26 and Up")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "WAGRIS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```



### 8 Inquiries Graduate Out-of-State Current Undergrads

```{r}
Eight <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Targeted OOS" & 
           #Student.Stage == "Inquiry" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year)&
           AgeGroup == "20-25")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "CUGROS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

### 9 Inquiries Graduate Out-of-State Working Adults

```{r}

Nine <- DAA4 %>% 
  filter(Stealth == "Not Stealth" & 
           Region == "Targeted OOS" & 
           #Student.Stage == "Inquiry" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year)& AgeGroup == "26 and Up")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Inq = sum(n))%>%
  pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Inquiries = sum(Applicant + Inquiry), Aud_P = "WAGROS") %>% 
  select(Anticipated.Start.Term.Year, Inquiries, Aud_P)
```

## Applications

### 10 Applications Undergraduate Degree for In-State High School Students Applicants


```{r}
Ten <- DAA4 %>% 
  filter(Region == "Maine" & 
           Student.Stage == "Applicant" & 
           Career == "Undergraduate" & 
           Student.Type == "First-Year Student" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup == "19 and Under")  %>% 
  group_by( Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "HSUGIS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)

```

### 11 Applicants Undergraduate Degree for Out-of-State High School Students




```{r}
Eleven <- DAA4 %>% 
  filter(Region == "Targeted OOS" & 
           Student.Stage == "Applicant" & 
           Career == "Undergraduate" & 
           Student.Type == "First-Year Student" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup == "19 and Under")  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "HSUGOS") %>% 
  select(Anticipated.Start.Term.Year, Applicants,Aud_P)
```

### 12 Applicants Transfer In-State



```{r}
Twelve <- DAA4 %>% 
  filter(Region == "Maine" & 
           Student.Stage == "Applicant" & 
           Career == "Undergraduate" & 
           Student.Type == "Transfer" & 
           grepl("^Fall", Anticipated.Start.Term.Year), 
           AgeGroupforTransfers %in% AgeTransfers)  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "CUTRIS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)
```

### 13 Applicants Transfer Out-of-State

```{r}
Thirteen <- DAA4 %>% 
  filter(Region == "Targeted OOS" & 
           Student.Stage == "Applicant" &
           Career == "Undergraduate" & 
           Student.Type == "Transfer" & 
           grepl("^Fall", Anticipated.Start.Term.Year), 
         AgeGroupforTransfers %in% AgeTransfers)  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  #pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "CUTROS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)

```




### 14 Applicants Working Adults 


```{r}
Fourteen <- DAA4 %>% 
  filter(#Region == "Targeted OOS" & 
           Student.Stage == "Applicant" &
           Career == "Undergraduate" & 
           #Student.Type == "Transfer" & 
           grepl("^Fall", Anticipated.Start.Term.Year), 
         AgeGroup %in% filterForWA)  %>% 
  group_by(Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  #pivot_wider(names_from = Student.Stage, values_from = Inq) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "WADC") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)
```

### 15 Applicants Graduate In-State CU

```{r}
Fifteen <- DAA4 %>% 
  filter(Region == "Maine" & 
           Student.Stage == "Applicant" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup ==  "20-25")  %>% 
  group_by( Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "CUGRIS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)
```

### 16 Applicants Graduate In-State WA

```{r}
Sixteen <- DAA4 %>% 
  filter(Region == "Maine" & 
           Student.Stage == "Applicant" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup == "26 and Up")  %>% 
  group_by( Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "WAGRIS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)
```

### 17 Applicants Graduate Out-of-State CU

```{r}
Seventeen <- DAA4 %>% 
  filter(Region == "Targeted OOS" & 
           Student.Stage == "Applicant" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup ==  "20-25")  %>% 
  group_by( Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "CUGROS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)
```

### 18 Applicants Graduate Out-of-State WA

```{r}
Eighteen <- DAA4 %>% 
  filter(Region == "Targeted OOS" & 
           Student.Stage == "Applicant" & 
           Career == "Graduate" & 
           Student.Type == "Graduate" & 
           grepl("^Fall", Anticipated.Start.Term.Year), AgeGroup ==  "26 and Up")  %>% 
  group_by( Anticipated.Start.Term.Year, Student.Stage) %>% 
  summarise(Applicants = sum(n))%>%
  # pivot_wider(names_from = Student.Stage, values_from = Applicants) %>% 
  mutate(Applicants = sum(Applicants), Aud_P = "WAGROS") %>% 
  select(Anticipated.Start.Term.Year, Applicants, Aud_P)

```

```{r}
# Nine[4,1] <- "Fall 2021"
# Nine[4,2] <- 0
# Nine[4,3] <- "WAGROS"
# dim(Nine)
HSUGIS <- merge.data.frame(One, Ten, all = T)
HSUGOS <- merge.data.frame(Two, Eleven, all = T)
CUTRIS <- merge.data.frame(Three, Twelve, all = T)
CUTROS <- merge.data.frame(Four, Thirteen, all = T)
WADC <- merge.data.frame(Five, Fourteen, all = T)

CUGRIS <- merge.data.frame(Six, Fifteen, all = T)
WAGRIS <- merge.data.frame(Seven, Sixteen, all = T)
CUGROS <- merge.data.frame(Eight, Seventeen, all = T)
WAGROS <- merge.data.frame(Nine, Eighteen, all = T)


I_AllFunnel <- rbind.data.frame(One, Two, Three, Four, Five, Six, Seven, Eight, Nine)

A_AllFunnel <- rbind.data.frame(Ten, Eleven, Twelve, Thirteen, Fourteen, Fifteen, Sixteen, Seventeen, Eighteen)



AllFunnelIandA <- merge.data.frame(I_AllFunnel, A_AllFunnel, all=T)

AllFunnelIandA <- AllFunnelIandA %>% mutate(DateCollected = Date)



# AllFunnelIandA <- AllFunnelIandA %>% mutate(DateCollected = as.Date("2020-11-17"))

# ,, Ten, Eleven Three, Four, Five, Six, Seven, Eight, Nine, Ten, Eleven, Twelve, Thirteen, Fourteen, Fifteen, Sixteen, Seventeen, Eighteen
# all <- all[,c(1:2, )]

  
kable(AllFunnelIandA)  

#write.csv(AllFunnelIandA, "C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/FinalDatatoAppend/AllGood.csv", row.names = F)


write.table(AllFunnelIandA,  
             file="C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/FinalDatatoAppend/AllGood.csv", 
             append = T, 
             sep=',', 
             row.names=T, 
             col.names=F )


#write.csv(AllFunnelIandA, "C:/Users/christine.iyer/Box/FY21 Weekly Admissions Reports Summary to Inform Agency Campaigns/FinalDatatoAppend/AllGood.csv", append = TRUE)

```

ggplot(data1, aes(x = date)) +
  geom_line(aes(y = x_r), size = 2, color = "red") + 
  geom_line(aes(y = reer), size = 2, color = "blue") +
  facet_wrap(.~origin, ncol = 4, scales = "free_y") + 
  scale_y_continuous(
    name = "X/GDP",
    sec.axis = sec_axis(~.*scaleFactor, name = "REER")
  ) +   
  theme_bw() +
  theme(
    axis.title.y = element_text(color = "red", size = 13),
    axis.title.y.right = element_text(color = "blue", size = 13)
  ) +
  ggtitle("Export Ratio and Real Effective Exchange Rate")


```{r}

AllFunnelIandA %>% 
  filter(Anticipated.Start.Term.Year == "Fall 2021") %>% 
  arrange(Aud_P) %>% 
  ggplot(aes(x = DateCollected)) +
  geom_line(aes(y = Inquiries), size = 3, color = "red") + 
  geom_line(aes(y = Applicants), size = 3, color = "blue")  +
  facet_wrap(~Aud_P, ncol = 3)+
  theme_bw()
```


[Notes from Rinck Meeting](https://www.wrike.com/open.htm?id=589319926) Refer to notes before proceeding.

[Wrike Notes](https://www.wrike.com/open.htm?id=586459551)

[Wrike Project for Chris](https://www.wrike.com/open.htm?id=586545629)

[Github Project for Chris](https://github.com/edithbird/FY21-Weekly-Admissions-Reports-Summary)
